---
title: "R Notebook"
output: html_notebook
---

Set working directory
```{r}
#setwd("C:/Users/Bea/Desktop/WebValley2022Netflix")
library(dplyr)
library(lubridate)
library(ggplot2)
library(stringr)
```

Some basic commands
```{r}
x <- c(1,-2,3,NA,NA,6,7,8,9,10)
print(x)
b = c(10.4, 5.6, 3.1, 6.4, 21.7)
is.na(x)
y <- x[!is.na(x)]
print(y)
x[6]
x[1:10]
```

Read the data
```{r}
netflix <- read.csv('Netflix.csv', header = T, row.names = 1)
netflix
```

explore the data frame
```{r}
str(netflix)
```

Transform variable in factor
```{r}
netflix$type <- factor(netflix$type)
netflix$age_certification<- factor(netflix$age_certification)
```


```{r}
summary(netflix)
```

TYPE OF CONTENT
Total number of movie and show
```{r}
table(netflix$type)
```
explore if here are some Na values
```{r}
table(is.na(netflix$type))
```

plot the distribution of content type
```{r}
barplot(table(netflix[3]),
        main = "Content type distribution in Netflix",
        xlab = "Type",
        ylab = "Freq",
        col = "greenyellow")
```

AGE CERTIFICATION
G: General Audiences, All Ages Admitted.
PG: Parental Guidance Suggested, Some Material May Not Be Suitable for Children.
PG-13: Parents Strongly Cautioned, Some Material May Be Inappropriate for Children Under 13.
R: Restricted, Children Under 17 Require Accompanying Parent or Adult Guardian.
NC-17: No One 17 and Under Admitted.
TV-Y (All Children)
TV-Y7 (Directed To Older Children) This program is designed for children age 7 and above.
TV-G (General Audience) Most parents would find this program suitable for all ages.
TV-PG (Parental Guidance Suggested) This program contains material that parents may find unsuitable for younger children.
TV-14 (Parents Strongly Cautioned) This program contains some material that many parents would find unsuitable for children under 13 years of age.
TV-MA (Mature Accompaniment) This program does not allow

explore if here are some Na values
```{r}
table(is.na(netflix$age_certification))
```

Total number of content stratified for age certification
```{r}
table(netflix$age_certification)
```
```{r}
netflix %>%
  group_by(age_certification) %>%
  #filter(!is.na(age_certification)) %>%
  #group_by(Year,type) %>%
  summarise(total = n()) %>%
  ggplot() +
  theme_minimal() +
  geom_col(aes(
    x = age_certification,
    y = total
    #, fill = type))+
  ), fill = "greenyellow")+
  labs(title = "Number of Items per release year")
```

```{r}
for (i in 1:dim(netflix)[1])  {
  if (netflix$age_certification[i]== "")
    netflix$age_certification[i] = NA
}
```

```{r}
# netflix[netflix$age_certification == "", "age_certification"] <- NA
```


RELEASE YEAR
Number of Items added per year
```{r}
netflix %>%
  group_by(release_year) %>%
  #group_by(Year,type) %>%
  summarise(total = n()) %>%
  ggplot() +
  theme_minimal() +
  geom_col(aes(
    x = release_year,
    y = total
    #, fill = type))+
  ), fill = "greenyellow")+
  labs(title = "Number of Items per release year")
```


YEAR ADDED
Time series
check na values
```{r}
table(is.na(netflix$date_added))
```

Transform data_added in date format
```{r}
netflix <- netflix %>%
  mutate(date_added = mdy(date_added))
```

Create new variables starting from data_added
Getting each year, month and date separated
```{r}
netflix <- netflix %>%
  mutate(Year = year(date_added)) %>%
  mutate(Month = month(date_added, label = TRUE)) %>%
  mutate(Date = day(date_added)) %>%
  mutate(Day = wday(date_added, label = TRUE))
```

Number of Items added per year
```{r}
df_plot_1 <- netflix %>%
  group_by(Year) %>%
  #group_by(Year,type) %>%
  summarise(total = n())

ggplot(df_plot_1) +
  theme_minimal() +
  geom_col(aes(
    x = Year,
    y = total
    #, fill = type))+
  ), fill = "greenyellow")+
  labs(title = "Number of Items added per year")
```

Number of Items added each day of the week
```{r}
netflix %>%
  #filter(!is.na(Day)) %>%
  group_by(Day) %>%
  summarise(total = n()) %>%
  ggplot() +
  theme_minimal() +
  geom_col(aes(
    x = Day,
    y = total),
           fill="cornflowerblue")+
  labs(title = "Number of Items added each day of the week")
```

Let's analyse data by quarters

```{r}
df_plot_2 <- netflix %>%
  group_by(Year,  m=quarter(date_added)) %>%
  #group_by(Year,type) %>%
  summarise(total = n())%>%
  filter(!is.na(Year))
df_plot_2$YM = str_c(df_plot_2$Year,"-", df_plot_2$m)
```


```{r}
ggplot(data=df_plot_2, aes(x=YM, y=total, group=1)) +
  geom_line()+
  geom_point()+
  labs(
    x = "Year Added",
    y = "Count",
    title = "Number of Items added per year"
  )+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```



GENERE - list

An R list is an object consisting of an ordered collection of objects known as its components.
There is no particular need for the components to be of the same mode or type, and, for example, a list could consist of a numeric vector, a logical value, a matrix, a complex vector, a character array, a function, and so on.
```{r}
Lst <- list(name="Fred", wife="Mary", no.children=3, child.ages=c(5,7,10))
print(Lst)
Lst[[1]]
Lst[[4]][[1]]
```

```{r}
list <- as.list(netflix$genres)
string <- toString(list)
genres <- str_extract_all(string, "[a-z]+")
list_of_genres <- as.data.frame(genres, col.names = c("genre"))
top_genres <- list_of_genres %>%
  group_by(genre) %>%
  summarise(count = n())  %>%
  arrange(desc(count))
```


```{r}
ggplot(top_genres)+
  geom_col(aes(count, reorder(genre, count)), fill="#089BA3")+
  theme_minimal()+
  labs(title = "The count of vidios by genres")
```

IMDB score
```{r}
ggplot(netflix) +
  geom_point(aes(release_year, imdb_score, color=type), alpha = 0.5) +
  labs(title = "IMDB Score Distribution")
```

```{r}
netflix %>%
  filter(!is.na(tmdb_popularity)) %>%
  group_by(release_year) %>%
  summarise(Mean = mean(tmdb_popularity)) %>%
  ggplot()+
  geom_col(aes(release_year, Mean), fill="#089BA3")+
  theme_minimal()+
  labs(title = "")
```


```{r, warnings=False}
netflix$decade = NA

for (i in 1:dim(netflix)[1])  {
  netflix$decade[i] = netflix$release_year[i] - netflix$release_year[i] %% 10
}
```

```{r}
netflix %>%
  filter(!is.na(tmdb_popularity)) %>%
  group_by(decade) %>%
  summarise(Mean = mean(tmdb_popularity)) %>%
  ggplot()+
  geom_col(aes(decade, Mean), fill="#089BA3")+
  theme_minimal()+
  labs(title = "")
```
EXTRA for the curious and brave ones

```{r}
library(wordcloud)
library(tidytext)
desc_words_m <- netflix %>%
  filter(type == "MOVIE" ) %>%
  unnest_tokens(word, description) %>%
  anti_join(stop_words)

count_word <- desc_words_m %>%
  count(word, sort = TRUE)
```


```{r, warnings=False}
wordcloud(words = count_word$word,
          freq = count_word$n,
          min.freq = 50,
          max.words = nrow(count_word),
          random.order = FALSE,
          rot.per = 0.1,
          colors = brewer.pal(8, "Dark2")
)
```